Open-Set Domain Adaptation through Self-Supervision

### 2022-02-11 paper/main.tex
fixed center loss statement

Here ${\bf v_i}$ is the output of the penultimate layer of $R_1$,
$\gamma({\bf z}_i)$ is the centroid of the features associated to class $i$,
$||\cdot||_2^2$ is the $l$-2 norm and $\lambda_1$ is the weight associated with the center loss term.

>>>>

Here ${\bf v_i}$ is the output of the penultimate layer of $R_1$,
$\gamma({\bf z}_i)$ is the centroid of the features associated to class $i$
(notice that the centroid is relative to a different rotation class $i$ in the multi-head variant)
$||\cdot||_2^2$ is the $l$-2 norm and $\lambda_1$ is the weight associated with the center loss term.
